---
title: "H-1B Visa Restrictions and Wage Impact Analysis - Improved Code"
output: html_document
author: "Kiet Nguyen & Lien Tran"
date: "2025-04-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r load-libraries}
# Load required libraries
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(ggplot2)
library(broom)
library(naniar)      # For advanced missing data visualization
library(mice)        # For multiple imputation
library(zoo)         # For time series functions
```

## 1. Data Loading and Initial Processing

```{r data-loading}
# Read the main analysis dataset
analysis_data <- read_csv("~/Documents/GitHub/h1b-econ-paper/process_Rstudio/55-56_improved_processed_data_with_combined_naics.csv")

# Read and process the offshoring data
offshoring_data <- read_csv("/Users/kietnguyen/Downloads/offshoring.csv") %>%
  # Clean any commas in numeric values
  mutate(across(c(`2012`, `2013`, `2014`, `2015`, `2016`, `2017`, `2018`, `2019`, `2020`), 
                ~as.numeric(str_replace_all(., ",", ""))))

# Process unemployment data
# Read with all columns as character type to avoid type issues
unemployment_data <- read_csv("/Users/kietnguyen/Downloads/unemployment.csv", 
                              col_names = FALSE, 
                              col_types = cols(.default = "c"))  # All columns as character

# Extract the years row (row 2 in the file)
unemployment_years <- as.character(unemployment_data[2, ])

# Extract data rows (from row 3 onwards)
unemployment_values <- unemployment_data[3:nrow(unemployment_data), ]

# Get column names
col_names <- c("Code", "Name")
for (i in 3:11) {
  col_names <- c(col_names, paste0("total_", unemployment_years[i]))
}
col_names <- c(col_names, "empty")
for (i in 13:21) {
  col_names <- c(col_names, paste0("rate_", unemployment_years[i]))
}

# Set column names
colnames(unemployment_values) <- col_names

# Process union data
union_data <- read_csv("/Users/kietnguyen/Downloads/unionrate.csv", 
                       col_names = FALSE, 
                       col_types = cols(.default = "c"))  # All columns as character
```

## 2. Standardized Data Processing Functions

```{r data-processing-functions}
# Function to correctly handle combined NAICS codes
standardize_naics <- function(df) {
  df %>%
    mutate(
      naics_2digit = as.character(Code),
      # For special combined cases, explicitly handle them
      naics_2digit_for_join = case_when(
        naics_2digit == "31-33" ~ "31-33",
        naics_2digit == "44-45" ~ "44-45",
        naics_2digit == "48-49" ~ "48-49",
        naics_2digit == "55-56" ~ "55-56",
        # For regular codes or if it contains a hyphen but isn't one of the special cases
        str_detect(naics_2digit, "-") ~ str_replace(naics_2digit, "-.*", ""),
        TRUE ~ naics_2digit
      )
    )
}

# Function to extract union data for a specific year - improved with error handling
extract_union_data <- function(data, year, year_pos, members_pos, members_pct_pos, 
                              represented_pos, represented_pct_pos) {
  # Extract rows with actual data (row 4 onwards)
  union_rows <- data[4:nrow(data), ]
  
  # Extract key columns with validation
  result <- tryCatch({
    union_rows %>%
      select(1, 2, all_of(year_pos), all_of(members_pos), all_of(members_pct_pos), 
             all_of(represented_pos), all_of(represented_pct_pos)) %>%
      rename(
        Code = 1,
        Name = 2,
        union_total_employed = all_of(year_pos),
        union_members = all_of(members_pos),
        union_pct = all_of(members_pct_pos),
        represented = all_of(represented_pos),
        represented_pct = all_of(represented_pct_pos)
      )
  }, error = function(e) {
    # Return a dataframe with the right structure but no data if there's an error
    warning(paste("Error in union data extraction for year", year, ":", e$message))
    return(data.frame(
      Code = character(),
      Name = character(),
      union_total_employed = numeric(),
      union_members = numeric(),
      union_pct = numeric(),
      represented = numeric(),
      represented_pct = numeric()
    ))
  })
  
  # Add year column
  result$year <- as.integer(year)
  
  # Ensure all required columns exist (even if empty)
  required_cols <- c("Code", "Name", "union_total_employed", "union_members", 
                     "union_pct", "represented", "represented_pct", "year")
  missing_cols <- setdiff(required_cols, names(result))
  
  if (length(missing_cols) > 0) {
    for (col in missing_cols) {
      result[[col]] <- NA
    }
  }
  
  return(result)
}

# Function to clean numeric data - handles different formats
clean_numeric <- function(x) {
  if (is.character(x)) {
    x <- str_replace_all(x, "[,$%]", "")  # Remove commas, dollar signs, and percent signs
    x <- str_trim(x)  # Trim whitespace
    x <- suppressWarnings(as.numeric(x))  # Convert to numeric
  }
  return(x)
}

# Function to calculate H1B dependency with protection against division by zero
calculate_h1b_dependency <- function(h1b_workers, total_employment, cap = 0.50) {
  result <- ifelse(is.na(total_employment) | total_employment <= 0, 
                  NA, 
                  h1b_workers / total_employment)
  
  # Cap extremely high values (likely errors)
  result <- ifelse(is.na(result) | result <= cap, result, cap)
  
  return(result)
}
```

## 3. Improved Data Transformation and Processing

```{r transform-offshoring-data}
# Transform offshoring data to long format
offshoring_long <- offshoring_data %>%
  pivot_longer(
    cols = c(`2012`, `2013`, `2014`, `2015`, `2016`, `2017`, `2018`, `2019`, `2020`),
    names_to = "year",
    values_to = "offshoring_value"
  ) %>%
  mutate(year = as.integer(year))
```

```{r process-unemployment-data}
# Process each year separately to avoid type issues
unemployment_long_list <- list()

for (year in 2012:2020) {
  year_str <- as.character(year)
  
  # Extract relevant columns for this year
  total_col <- paste0("total_", year_str)
  rate_col <- paste0("rate_", year_str)
  
  # Skip if columns don't exist
  if (!(total_col %in% colnames(unemployment_values)) || 
      !(rate_col %in% colnames(unemployment_values))) {
    next
  }
  
  # Process year data
  year_data <- unemployment_values %>%
    select(Code, Name, !!total_col, !!rate_col) %>%
    rename(
      unemployment_total = !!total_col,
      unemployment_rate = !!rate_col
    ) %>%
    mutate(
      year = as.integer(year_str),
      # Clean and convert numeric data
      unemployment_total = clean_numeric(unemployment_total),
      unemployment_rate = clean_numeric(unemployment_rate)
    )
  
  unemployment_long_list[[year_str]] <- year_data
}

# Combine all years
unemployment_long <- bind_rows(unemployment_long_list)
```

```{r process-union-data}
# Based on the row examined, create a mapping of years to column positions
year_mapping <- list(
  "2020" = list(year_pos = 3, members_pos = 4, members_pct_pos = 5, represented_pos = 6, represented_pct_pos = 7),
  "2019" = list(year_pos = 8, members_pos = 9, members_pct_pos = 10, represented_pos = 11, represented_pct_pos = 12),
  "2018" = list(year_pos = 13, members_pos = 14, members_pct_pos = 15, represented_pos = 16, represented_pct_pos = 17),
  "2017" = list(year_pos = 18, members_pos = 19, members_pct_pos = 20, represented_pos = 21, represented_pct_pos = 22),
  "2016" = list(year_pos = 23, members_pos = 24, members_pct_pos = 25, represented_pos = 26, represented_pct_pos = 27),
  "2015" = list(year_pos = 28, members_pos = 29, members_pct_pos = 30, represented_pos = 31, represented_pct_pos = 32),
  "2014" = list(year_pos = 33, members_pos = 34, members_pct_pos = 35, represented_pos = 36, represented_pct_pos = 37),
  "2013" = list(year_pos = 38, members_pos = 39, members_pct_pos = 40, represented_pos = 41, represented_pct_pos = 42),
  "2012" = list(year_pos = 43, members_pos = 44, members_pct_pos = 45, represented_pos = 46, represented_pct_pos = 47)
)

# Process each year and add to a list
union_long_list <- list()

for (year in names(year_mapping)) {
  positions <- year_mapping[[year]]
  
  # Use tryCatch to handle potential errors
  tryCatch({
    year_data <- extract_union_data(
      union_data, 
      year = year,
      year_pos = positions$year_pos,
      members_pos = positions$members_pos,
      members_pct_pos = positions$members_pct_pos,
      represented_pos = positions$represented_pos,
      represented_pct_pos = positions$represented_pct_pos
    )
    
    union_long_list[[year]] <- year_data
  }, error = function(e) {
    warning(paste("Error processing union data for year", year, ":", e$message))
  })
}

# Combine all union data
union_long <- bind_rows(union_long_list)

# Clean numeric columns
union_long <- union_long %>%
  mutate(across(c(union_total_employed, union_members, union_pct, represented, represented_pct),
                ~clean_numeric(.)))
```

## 4. Standardize NAICS Codes and Join Datasets

```{r standardize-and-join}
# Apply NAICS standardization
unemployment_long <- standardize_naics(unemployment_long)
offshoring_long <- standardize_naics(offshoring_long)
union_long <- standardize_naics(union_long)

# When joining, use the new field for joining but keep the original format
# Ensure consistent type in analysis data
analysis_data <- analysis_data %>%
  mutate(
    year = as.integer(year),
    naics_2digit = as.character(naics_2digit),
    # Create the join key that will match the standardized codes
    naics_2digit_for_join = case_when(
      naics_2digit == "31-33" ~ "31-33",
      naics_2digit == "44-45" ~ "44-45",
      naics_2digit == "48-49" ~ "48-49",
      naics_2digit == "55-56" ~ "55-56",
      TRUE ~ naics_2digit
    )
  )

# Join datasets using the standardized joining field
# Modified to validate matching success
combined_data <- analysis_data %>%
  # Join with unemployment data
  left_join(
    unemployment_long %>% 
      select(year, naics_2digit_for_join, unemployment_total, unemployment_rate),
    by = c("year", "naics_2digit_for_join")
  ) %>%
  # Join with offshoring data
  left_join(
    offshoring_long %>% 
      select(year, naics_2digit_for_join, offshoring_value),
    by = c("year", "naics_2digit_for_join")
  ) %>%
  # Join with union data
  left_join(
    union_long %>% 
      select(year, naics_2digit_for_join, union_total_employed, union_members, union_pct, represented, represented_pct),
    by = c("year", "naics_2digit_for_join")
  )

# Check join success
join_success <- combined_data %>%
  group_by(year) %>%
  summarize(
    unemployment_missing = mean(is.na(unemployment_rate)) * 100,
    offshoring_missing = mean(is.na(offshoring_value)) * 100,
    union_missing = mean(is.na(union_pct)) * 100
  )

print(join_success)
```

## 5. Fix the Infinity Problem and Create Analytical Variables

```{r create-analytical-variables}
# Create analytical variables with improved handling of missing/problematic values
initial_dataset <- combined_data %>%
  # First, fix the h1b_dependency_current calculation
  mutate(
    # Fix h1b_dependency_current - cap at 50% max
    h1b_dependency_current_fixed = calculate_h1b_dependency(
      total_approvals, total_employment, cap = 0.50
    ),
    
    # Scale offshoring to be per 1000 employees instead of per employee
    offshoring_per_1000_employees = ifelse(
      !is.na(offshoring_value) & !is.na(total_employment) & total_employment > 0,
      (offshoring_value / total_employment) * 1000,
      NA
    ),
    
    # Keep the original for consistency with existing analysis
    h1b_dependency_current_original = h1b_dependency_current
  )

# Check the impact of our fix
cat("Before fix - summary of h1b_dependency_current:\n")
print(summary(initial_dataset$h1b_dependency_current_original))
cat("\nAfter fix - summary of h1b_dependency_current_fixed:\n")
print(summary(initial_dataset$h1b_dependency_current_fixed))
```

```{r create-additional-variables}
# Create the final dataset with all analytical variables
final_dataset <- initial_dataset %>%
  # Now create all analytical variables using the fixed dependency ratio
  mutate(
    # Use the fixed version for all calculations
    h1b_dependency_current = h1b_dependency_current_fixed,
    
    # Calculate unemployment-adjusted H1B dependency
    h1b_unemployment_ratio = ifelse(
      !is.na(unemployment_rate) & unemployment_rate > 0,
      h1b_dependency_current / (unemployment_rate/100),
      NA
    ),
    
    # Union impact variables - with protection against division by zero
    union_h1b_ratio = ifelse(
      !is.na(union_pct) & union_pct > 0,
      h1b_dependency_current / (union_pct/100),
      NA
    ),
    
    # Log transformations - adding 1 to handle zeros
    log_unemployment = ifelse(!is.na(unemployment_total), log(unemployment_total + 1), NA),
    log_offshoring = ifelse(!is.na(offshoring_value), log(offshoring_value + 1), NA),
    log_union = ifelse(!is.na(union_members), log(union_members + 1), NA),
    
    # IMPROVED: Create binary indicators - keep NAs as NAs, don't convert to FALSE
    high_unemployment = ifelse(
      !is.na(unemployment_rate),
      unemployment_rate > median(unemployment_rate, na.rm = TRUE),
      NA
    ),
    
    high_union = ifelse(
      !is.na(union_pct), 
      union_pct > median(union_pct, na.rm = TRUE),
      NA
    ),
    
    high_offshoring = ifelse(
      !is.na(offshoring_per_1000_employees),
      offshoring_per_1000_employees > median(offshoring_per_1000_employees, na.rm = TRUE),
      NA
    ),
    
    # Create interaction terms - now properly handling NAs
    did_unemployment = ifelse(
      !is.na(did_median) & !is.na(high_unemployment),
      did_median * as.integer(high_unemployment),
      NA
    ),
    
    did_union = ifelse(
      !is.na(did_median) & !is.na(high_union),
      did_median * as.integer(high_union),
      NA
    ),
    
    did_offshoring = ifelse(
      !is.na(did_median) & !is.na(high_offshoring),
      did_median * as.integer(high_offshoring),
      NA
    ),
    
    # Outlier handling for unemployment
    unemployment_rate_winsorized = ifelse(
      !is.na(unemployment_rate),
      pmin(pmax(unemployment_rate, 
                quantile(unemployment_rate, 0.05, na.rm = TRUE)),
           quantile(unemployment_rate, 0.95, na.rm = TRUE)),
      NA
    )
  )
```

## 6. Missing Data Analysis and Imputation

```{r missing-data-analysis}
# Create a visualization of missing data patterns
gg_miss_var(final_dataset[, c("unemployment_rate", "offshoring_value", 
                              "union_pct", "h1b_dependency_current")], 
            show_pct = TRUE)

# Count missing values
missing_summary <- final_dataset %>%
  summarise(across(everything(), ~sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "missing_count") %>%
  filter(missing_count > 0) %>%
  arrange(desc(missing_count))

print(missing_summary)
```

```{r imputation-setup}
# Identify variables for imputation 
vars_to_impute <- c("union_pct", "offshoring_per_1000_employees")

# Create a subset for imputation
impute_data <- final_dataset %>%
  select(year, naics_2digit, unemployment_rate, union_pct, offshoring_per_1000_employees,
         h1b_dependency_current, total_approvals, total_denials, denial_rate)

# Set up the imputation method
impute_method <- make.method(impute_data)
impute_method[vars_to_impute] <- "pmm"  # Predictive mean matching

# Run the imputation
set.seed(123)  # For reproducibility
imputed_data <- mice(impute_data, method = impute_method, m = 5, maxit = 10, printFlag = FALSE)

# Get the first imputed dataset as an example
imputed_dataset <- complete(imputed_data, 1)
```

```{r merge-imputed-data}
# Merge imputed variables back to the main dataset
final_dataset_with_imputation <- final_dataset %>%
  # Create columns for imputed values
  mutate(
    union_pct_imputed = imputed_dataset$union_pct[match(paste(year, naics_2digit), 
                                                       paste(imputed_dataset$year, imputed_dataset$naics_2digit))],
    offshoring_per_1000_employees_imputed = imputed_dataset$offshoring_per_1000_employees[
      match(paste(year, naics_2digit), paste(imputed_dataset$year, imputed_dataset$naics_2digit))
    ],
    
    # Create a flag for whether we used imputed values
    using_imputed_union = is.na(union_pct),
    using_imputed_offshoring = is.na(offshoring_per_1000_employees)
  )

# Use either original or imputed values
final_dataset_complete <- final_dataset_with_imputation %>%
  mutate(
    union_pct_combined = ifelse(is.na(union_pct), union_pct_imputed, union_pct),
    offshoring_per_1000_employees_combined = ifelse(
      is.na(offshoring_per_1000_employees), 
      offshoring_per_1000_employees_imputed, 
      offshoring_per_1000_employees
    )
  )
```

## 7. Check for Outliers and Data Quality

```{r outlier-analysis}
# Check distribution of key variables
key_vars <- c("denial_rate", "unemployment_rate", "offshoring_per_1000_employees_combined", 
              "union_pct_combined", "h1b_dependency_current", "real_wage")

# Plot histograms for key variables
lapply(key_vars, function(var) {
  if (var %in% colnames(final_dataset_complete)) {
    ggplot(final_dataset_complete, aes_string(x = var)) +
      geom_histogram(bins = 20, fill = "steelblue", alpha = 0.7) +
      theme_minimal() +
      labs(title = paste("Distribution of", var))
  }
})

# Identify outliers using the IQR method
outlier_summary <- lapply(key_vars, function(var) {
  if (var %in% colnames(final_dataset_complete)) {
    x <- final_dataset_complete[[var]]
    x <- x[!is.na(x)]
    q1 <- quantile(x, 0.25)
    q3 <- quantile(x, 0.75)
    iqr <- q3 - q1
    lower_bound <- q1 - 1.5 * iqr
    upper_bound <- q3 + 1.5 * iqr
    outliers <- x[x < lower_bound | x > upper_bound]
    data.frame(
      variable = var,
      n_outliers = length(outliers),
      pct_outliers = length(outliers) / length(x) * 100,
      min_outlier = min(outliers, na.rm = TRUE),
      max_outlier = max(outliers, na.rm = TRUE)
    )
  }
})

outlier_df <- do.call(rbind, outlier_summary)
print(outlier_df)
```

## 8. Save Final Dataset

```{r save-datasets}
# Save both versions of the dataset
write_csv(final_dataset, "~/Documents/GitHub/h1b-econ-paper/process_Rstudio/combined_labor_market_analysis_data_original.csv")
write_csv(final_dataset_complete, "~/Documents/GitHub/h1b-econ-paper/process_Rstudio/combined_labor_market_analysis_data_imputed.csv")

# Print summary information
cat("\n=== Data Processing Complete ===\n")
cat("Original dataset saved as 'combined_labor_market_analysis_data_original.csv'\n")
cat("Imputed dataset saved as 'combined_labor_market_analysis_data_imputed.csv'\n")
cat("Number of observations:", nrow(final_dataset_complete), "\n")
cat("Number of variables:", ncol(final_dataset_complete), "\n\n")
```

## 9. Test Robustness of Your DiD Model

```{r did-robustness}
# Run different specifications of your DiD model

# Base model
model1 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median,
            data = final_dataset_complete)

# With controls
model2 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median +
               unemployment_rate_winsorized + offshoring_per_1000_employees_combined,
            data = final_dataset_complete)

# With imputed union data
model3 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median +
               unemployment_rate_winsorized + offshoring_per_1000_employees_combined,
            data = final_dataset_complete)

# # With fixed effects using factors
# model4 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median +
#                unemployment_rate_winsorized + offshoring_per_1000_employees_combined + 
#                factor(naics_2digit) + factor(year),
#             data = final_dataset_complete)

# With fixed effects using factors
model4 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median + factor(naics_2digit) + inflation_rate,
            data = final_dataset_complete)

# Compare models
model_comparison <- list(
  Original = model1,
  With_Controls = model2,
  With_Union = model3,
  With_FE = model4
) %>%
  lapply(tidy) %>%
  bind_rows(.id = "model") %>%
  filter(term %in% c("denial_rate", "high_dependency_median", "did_median")) %>%
  select(model, term, estimate, std.error, p.value)

print(model_comparison)
```

## 10. Visualize Key Findings

```{r visualize-findings}
# Create a visualization of the DiD effect

# Prepare data for visualization
plot_data <- final_dataset_complete %>%
  group_by(year, high_dependency_median) %>%
  summarize(avg_log_wage = mean(log_real_wage, na.rm = TRUE),
            avg_denial_rate = mean(denial_rate, na.rm = TRUE),
            .groups = "drop") %>%
  mutate(treatment_group = ifelse(high_dependency_median, "High H-1B Dependency", "Low H-1B Dependency"))

# Plot the DiD
ggplot(plot_data, aes(x = year, y = avg_log_wage, color = treatment_group, group = treatment_group)) +
  geom_line(size = 1) +
  geom_vline(xintercept = 2017, linetype = "dashed", color = "red") +
  annotate("text", x = 2017, y = min(plot_data$avg_log_wage), label = "Buy American, Hire American", 
           angle = 90, vjust = -0.5, hjust = -0.2) +
  theme_minimal() +
  labs(
    title = "Difference-in-Differences: Log Real Wage by H-1B Dependency",
    subtitle = "Before and After the 'Buy American, Hire American' Executive Order",
    x = "Year",
    y = "Average Log Real Wage",
    color = "Industry Group"
  )
```