---
title: "H-1B Visa Restrictions and Wage Impact Analysis - Improved Code"
output: html_document
author: "Kiet Nguyen & Lien Tran"
date: "2025-04-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r load-libraries}
# Load required libraries
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(ggplot2)
library(broom)
library(naniar)      # For advanced missing data visualization
library(mice)        # For multiple imputation
library(zoo)         # For time series functions
```

## 1. Data Loading and Initial Processing

```{r data-loading}
# Read the main analysis dataset
analysis_data <- read_csv("~/Documents/GitHub/h1b-econ-paper/process_Rstudio/55-56_improved_processed_data_with_combined_naics.csv")

# Read and process the offshoring data
offshoring_data <- read_csv("/Users/kietnguyen/Downloads/offshoring.csv") %>%
  # Clean any commas in numeric values
  mutate(across(c(`2012`, `2013`, `2014`, `2015`, `2016`, `2017`, `2018`, `2019`, `2020`), 
                ~as.numeric(str_replace_all(., ",", ""))))

# Process unemployment data
# Read with all columns as character type to avoid type issues
unemployment_data <- read_csv("/Users/kietnguyen/Downloads/unemployment.csv", 
                              col_names = FALSE, 
                              col_types = cols(.default = "c"))  # All columns as character

# Extract the years row (row 2 in the file)
unemployment_years <- as.character(unemployment_data[2, ])

# Extract data rows (from row 3 onwards)
unemployment_values <- unemployment_data[3:nrow(unemployment_data), ]

# Get column names
col_names <- c("Code", "Name")
for (i in 3:11) {
  col_names <- c(col_names, paste0("total_", unemployment_years[i]))
}
col_names <- c(col_names, "empty")
for (i in 13:21) {
  col_names <- c(col_names, paste0("rate_", unemployment_years[i]))
}

# Set column names
colnames(unemployment_values) <- col_names

# Process union data
union_data <- read_csv("/Users/kietnguyen/Downloads/unionrate.csv", 
                       col_names = FALSE, 
                       col_types = cols(.default = "c"))  # All columns as character
```

## 2. Standardized Data Processing Functions

```{r data-processing-functions}
# Function to correctly handle combined NAICS codes
standardize_naics <- function(df) {
  df %>%
    mutate(
      naics_2digit = as.character(Code),
      # For special combined cases, explicitly handle them
      naics_2digit_for_join = case_when(
        naics_2digit == "31-33" ~ "31-33",
        naics_2digit == "44-45" ~ "44-45",
        naics_2digit == "48-49" ~ "48-49",
        naics_2digit == "55-56" ~ "55-56",
        # For regular codes or if it contains a hyphen but isn't one of the special cases
        str_detect(naics_2digit, "-") ~ str_replace(naics_2digit, "-.*", ""),
        TRUE ~ naics_2digit
      )
    )
}

# Function to extract union data for a specific year - improved with error handling
extract_union_data <- function(data, year, year_pos, members_pos, members_pct_pos, 
                              represented_pos, represented_pct_pos) {
  # Extract rows with actual data (row 4 onwards)
  union_rows <- data[4:nrow(data), ]
  
  # Extract key columns with validation
  result <- tryCatch({
    union_rows %>%
      select(1, 2, all_of(year_pos), all_of(members_pos), all_of(members_pct_pos), 
             all_of(represented_pos), all_of(represented_pct_pos)) %>%
      rename(
        Code = 1,
        Name = 2,
        union_total_employed = all_of(year_pos),
        union_members = all_of(members_pos),
        union_pct = all_of(members_pct_pos),
        represented = all_of(represented_pos),
        represented_pct = all_of(represented_pct_pos)
      )
  }, error = function(e) {
    # Return a dataframe with the right structure but no data if there's an error
    warning(paste("Error in union data extraction for year", year, ":", e$message))
    return(data.frame(
      Code = character(),
      Name = character(),
      union_total_employed = numeric(),
      union_members = numeric(),
      union_pct = numeric(),
      represented = numeric(),
      represented_pct = numeric()
    ))
  })
  
  # Add year column
  result$year <- as.integer(year)
  
  # Ensure all required columns exist (even if empty)
  required_cols <- c("Code", "Name", "union_total_employed", "union_members", 
                     "union_pct", "represented", "represented_pct", "year")
  missing_cols <- setdiff(required_cols, names(result))
  
  if (length(missing_cols) > 0) {
    for (col in missing_cols) {
      result[[col]] <- NA
    }
  }
  
  return(result)
}

# Function to clean numeric data - handles different formats
clean_numeric <- function(x) {
  if (is.character(x)) {
    x <- str_replace_all(x, "[,$%]", "")  # Remove commas, dollar signs, and percent signs
    x <- str_trim(x)  # Trim whitespace
    x <- suppressWarnings(as.numeric(x))  # Convert to numeric
  }
  return(x)
}

# Function to calculate H1B dependency with protection against division by zero
calculate_h1b_dependency <- function(h1b_workers, total_employment, cap = 0.50) {
  result <- ifelse(is.na(total_employment) | total_employment <= 0, 
                  NA, 
                  h1b_workers / total_employment)
  
  # Cap extremely high values (likely errors)
  result <- ifelse(is.na(result) | result <= cap, result, cap)
  
  return(result)
}
```

## 3. Improved Data Transformation and Processing

```{r transform-offshoring-data}
# Transform offshoring data to long format
offshoring_long <- offshoring_data %>%
  pivot_longer(
    cols = c(`2012`, `2013`, `2014`, `2015`, `2016`, `2017`, `2018`, `2019`, `2020`),
    names_to = "year",
    values_to = "offshoring_value"
  ) %>%
  mutate(year = as.integer(year))
```

```{r process-unemployment-data}
# Process each year separately to avoid type issues
unemployment_long_list <- list()

for (year in 2012:2020) {
  year_str <- as.character(year)
  
  # Extract relevant columns for this year
  total_col <- paste0("total_", year_str)
  rate_col <- paste0("rate_", year_str)
  
  # Skip if columns don't exist
  if (!(total_col %in% colnames(unemployment_values)) || 
      !(rate_col %in% colnames(unemployment_values))) {
    next
  }
  
  # Process year data
  year_data <- unemployment_values %>%
    select(Code, Name, !!total_col, !!rate_col) %>%
    rename(
      unemployment_total = !!total_col,
      unemployment_rate = !!rate_col
    ) %>%
    mutate(
      year = as.integer(year_str),
      # Clean and convert numeric data
      unemployment_total = clean_numeric(unemployment_total),
      unemployment_rate = clean_numeric(unemployment_rate)
    )
  
  unemployment_long_list[[year_str]] <- year_data
}

# Combine all years
unemployment_long <- bind_rows(unemployment_long_list)
```

```{r process-union-data}
# Based on the row examined, create a mapping of years to column positions
year_mapping <- list(
  "2020" = list(year_pos = 3, members_pos = 4, members_pct_pos = 5, represented_pos = 6, represented_pct_pos = 7),
  "2019" = list(year_pos = 8, members_pos = 9, members_pct_pos = 10, represented_pos = 11, represented_pct_pos = 12),
  "2018" = list(year_pos = 13, members_pos = 14, members_pct_pos = 15, represented_pos = 16, represented_pct_pos = 17),
  "2017" = list(year_pos = 18, members_pos = 19, members_pct_pos = 20, represented_pos = 21, represented_pct_pos = 22),
  "2016" = list(year_pos = 23, members_pos = 24, members_pct_pos = 25, represented_pos = 26, represented_pct_pos = 27),
  "2015" = list(year_pos = 28, members_pos = 29, members_pct_pos = 30, represented_pos = 31, represented_pct_pos = 32),
  "2014" = list(year_pos = 33, members_pos = 34, members_pct_pos = 35, represented_pos = 36, represented_pct_pos = 37),
  "2013" = list(year_pos = 38, members_pos = 39, members_pct_pos = 40, represented_pos = 41, represented_pct_pos = 42),
  "2012" = list(year_pos = 43, members_pos = 44, members_pct_pos = 45, represented_pos = 46, represented_pct_pos = 47)
)

# Process each year and add to a list
union_long_list <- list()

for (year in names(year_mapping)) {
  positions <- year_mapping[[year]]
  
  # Use tryCatch to handle potential errors
  tryCatch({
    year_data <- extract_union_data(
      union_data, 
      year = year,
      year_pos = positions$year_pos,
      members_pos = positions$members_pos,
      members_pct_pos = positions$members_pct_pos,
      represented_pos = positions$represented_pos,
      represented_pct_pos = positions$represented_pct_pos
    )
    
    union_long_list[[year]] <- year_data
  }, error = function(e) {
    warning(paste("Error processing union data for year", year, ":", e$message))
  })
}

# Combine all union data
union_long <- bind_rows(union_long_list)

# Clean numeric columns
union_long <- union_long %>%
  mutate(across(c(union_total_employed, union_members, union_pct, represented, represented_pct),
                ~clean_numeric(.)))
```

## 4. Standardize NAICS Codes and Join Datasets

```{r standardize-and-join}
# Apply NAICS standardization
unemployment_long <- standardize_naics(unemployment_long)
offshoring_long <- standardize_naics(offshoring_long)
union_long <- standardize_naics(union_long)

# When joining, use the new field for joining but keep the original format
# Ensure consistent type in analysis data
analysis_data <- analysis_data %>%
  mutate(
    year = as.integer(year),
    naics_2digit = as.character(naics_2digit),
    # Create the join key that will match the standardized codes
    naics_2digit_for_join = case_when(
      naics_2digit == "31-33" ~ "31-33",
      naics_2digit == "44-45" ~ "44-45",
      naics_2digit == "48-49" ~ "48-49",
      naics_2digit == "55-56" ~ "55-56",
      TRUE ~ naics_2digit
    )
  )

# Join datasets using the standardized joining field
# Modified to validate matching success
combined_data <- analysis_data %>%
  # Join with unemployment data
  left_join(
    unemployment_long %>% 
      select(year, naics_2digit_for_join, unemployment_total, unemployment_rate),
    by = c("year", "naics_2digit_for_join")
  ) %>%
  # Join with offshoring data
  left_join(
    offshoring_long %>% 
      select(year, naics_2digit_for_join, offshoring_value),
    by = c("year", "naics_2digit_for_join")
  ) %>%
  # Join with union data
  left_join(
    union_long %>% 
      select(year, naics_2digit_for_join, union_total_employed, union_members, union_pct, represented, represented_pct),
    by = c("year", "naics_2digit_for_join")
  )

# Check join success
join_success <- combined_data %>%
  group_by(year) %>%
  summarize(
    unemployment_missing = mean(is.na(unemployment_rate)) * 100,
    offshoring_missing = mean(is.na(offshoring_value)) * 100,
    union_missing = mean(is.na(union_pct)) * 100
  )

print(join_success)
```

## 5. Fix the Infinity Problem and Create Analytical Variables

```{r create-analytical-variables}
# Create analytical variables with improved handling of missing/problematic values
initial_dataset <- combined_data %>%
  # First, fix the h1b_dependency_current calculation
  mutate(
    # Fix h1b_dependency_current - cap at 50% max
    h1b_dependency_current_fixed = calculate_h1b_dependency(
      total_approvals, total_employment, cap = 0.50
    ),
    
    # Scale offshoring to be per 1000 employees instead of per employee
    offshoring_per_1000_employees = ifelse(
      !is.na(offshoring_value) & !is.na(total_employment) & total_employment > 0,
      (offshoring_value / total_employment) * 1000,
      NA
    ),
    
    # Keep the original for consistency with existing analysis
    h1b_dependency_current_original = h1b_dependency_current
  )

# Check the impact of our fix
cat("Before fix - summary of h1b_dependency_current:\n")
print(summary(initial_dataset$h1b_dependency_current_original))
cat("\nAfter fix - summary of h1b_dependency_current_fixed:\n")
print(summary(initial_dataset$h1b_dependency_current_fixed))
```

```{r create-additional-variables}
# Create the final dataset with all analytical variables
final_dataset <- initial_dataset %>%
  # Now create all analytical variables using the fixed dependency ratio
  mutate(
    # Use the fixed version for all calculations
    h1b_dependency_current = h1b_dependency_current_fixed,
    
    # Calculate unemployment-adjusted H1B dependency
    h1b_unemployment_ratio = ifelse(
      !is.na(unemployment_rate) & unemployment_rate > 0,
      h1b_dependency_current / (unemployment_rate/100),
      NA
    ),
    
    # Union impact variables - with protection against division by zero
    union_h1b_ratio = ifelse(
      !is.na(union_pct) & union_pct > 0,
      h1b_dependency_current / (union_pct/100),
      NA
    ),
    
    # Log transformations - adding 1 to handle zeros
    log_unemployment = ifelse(!is.na(unemployment_total), log(unemployment_total + 1), NA),
    log_offshoring = ifelse(!is.na(offshoring_value), log(offshoring_value + 1), NA),
    log_union = ifelse(!is.na(union_members), log(union_members + 1), NA),
    
    # IMPROVED: Create binary indicators - keep NAs as NAs, don't convert to FALSE
    high_unemployment = ifelse(
      !is.na(unemployment_rate),
      unemployment_rate > median(unemployment_rate, na.rm = TRUE),
      NA
    ),
    
    high_union = ifelse(
      !is.na(union_pct), 
      union_pct > median(union_pct, na.rm = TRUE),
      NA
    ),
    
    high_offshoring = ifelse(
      !is.na(offshoring_per_1000_employees),
      offshoring_per_1000_employees > median(offshoring_per_1000_employees, na.rm = TRUE),
      NA
    ),
    
    # Create interaction terms - now properly handling NAs
    did_unemployment = ifelse(
      !is.na(did_median) & !is.na(high_unemployment),
      did_median * as.integer(high_unemployment),
      NA
    ),
    
    did_union = ifelse(
      !is.na(did_median) & !is.na(high_union),
      did_median * as.integer(high_union),
      NA
    ),
    
    did_offshoring = ifelse(
      !is.na(did_median) & !is.na(high_offshoring),
      did_median * as.integer(high_offshoring),
      NA
    ),
    
    # Outlier handling for unemployment
    unemployment_rate_winsorized = ifelse(
      !is.na(unemployment_rate),
      pmin(pmax(unemployment_rate, 
                quantile(unemployment_rate, 0.05, na.rm = TRUE)),
           quantile(unemployment_rate, 0.95, na.rm = TRUE)),
      NA
    )
  )
```

## 6. Missing Data Analysis and Imputation

```{r missing-data-analysis}
# Create a visualization of missing data patterns
gg_miss_var(final_dataset[, c("unemployment_rate", "offshoring_value", 
                              "union_pct", "h1b_dependency_current")], 
            show_pct = TRUE)

# Count missing values
missing_summary <- final_dataset %>%
  summarise(across(everything(), ~sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "missing_count") %>%
  filter(missing_count > 0) %>%
  arrange(desc(missing_count))

print(missing_summary)
```

```{r imputation-setup}
# Identify variables for imputation 
vars_to_impute <- c("union_pct", "offshoring_per_1000_employees")

# Create a subset for imputation
impute_data <- final_dataset %>%
  select(year, naics_2digit, unemployment_rate, union_pct, offshoring_per_1000_employees,
         h1b_dependency_current, total_approvals, total_denials, denial_rate)

# Set up the imputation method
impute_method <- make.method(impute_data)
impute_method[vars_to_impute] <- "pmm"  # Predictive mean matching

# Run the imputation
set.seed(123)  # For reproducibility
imputed_data <- mice(impute_data, method = impute_method, m = 5, maxit = 10, printFlag = FALSE)

# Get the first imputed dataset as an example
imputed_dataset <- complete(imputed_data, 1)
```

```{r merge-imputed-data}
# Merge imputed variables back to the main dataset
final_dataset_with_imputation <- final_dataset %>%
  # Create columns for imputed values
  mutate(
    union_pct_imputed = imputed_dataset$union_pct[match(paste(year, naics_2digit), 
                                                       paste(imputed_dataset$year, imputed_dataset$naics_2digit))],
    offshoring_per_1000_employees_imputed = imputed_dataset$offshoring_per_1000_employees[
      match(paste(year, naics_2digit), paste(imputed_dataset$year, imputed_dataset$naics_2digit))
    ],
    
    # Create a flag for whether we used imputed values
    using_imputed_union = is.na(union_pct),
    using_imputed_offshoring = is.na(offshoring_per_1000_employees)
  )

# Use either original or imputed values
final_dataset_complete <- final_dataset_with_imputation %>%
  mutate(
    union_pct_combined = ifelse(is.na(union_pct), union_pct_imputed, union_pct),
    offshoring_per_1000_employees_combined = ifelse(
      is.na(offshoring_per_1000_employees), 
      offshoring_per_1000_employees_imputed, 
      offshoring_per_1000_employees
    )
  )
```

## 7. Check for Outliers and Data Quality

```{r outlier-analysis}
# Check distribution of key variables
key_vars <- c("denial_rate", "unemployment_rate", "offshoring_per_1000_employees_combined", 
              "union_pct_combined", "h1b_dependency_current", "real_wage")

# Plot histograms for key variables
lapply(key_vars, function(var) {
  if (var %in% colnames(final_dataset_complete)) {
    ggplot(final_dataset_complete, aes_string(x = var)) +
      geom_histogram(bins = 20, fill = "steelblue", alpha = 0.7) +
      theme_minimal() +
      labs(title = paste("Distribution of", var))
  }
})

# Identify outliers using the IQR method
outlier_summary <- lapply(key_vars, function(var) {
  if (var %in% colnames(final_dataset_complete)) {
    x <- final_dataset_complete[[var]]
    x <- x[!is.na(x)]
    q1 <- quantile(x, 0.25)
    q3 <- quantile(x, 0.75)
    iqr <- q3 - q1
    lower_bound <- q1 - 1.5 * iqr
    upper_bound <- q3 + 1.5 * iqr
    outliers <- x[x < lower_bound | x > upper_bound]
    data.frame(
      variable = var,
      n_outliers = length(outliers),
      pct_outliers = length(outliers) / length(x) * 100,
      min_outlier = min(outliers, na.rm = TRUE),
      max_outlier = max(outliers, na.rm = TRUE)
    )
  }
})

outlier_df <- do.call(rbind, outlier_summary)
print(outlier_df)
```

## 8. Save Final Dataset

```{r save-datasets}
# Save both versions of the dataset
write_csv(final_dataset, "~/Documents/GitHub/h1b-econ-paper/process_Rstudio/combined_labor_market_analysis_data_original.csv")
write_csv(final_dataset_complete, "~/Documents/GitHub/h1b-econ-paper/process_Rstudio/combined_labor_market_analysis_data_imputed.csv")

# Print summary information
cat("\n=== Data Processing Complete ===\n")
cat("Original dataset saved as 'combined_labor_market_analysis_data_original.csv'\n")
cat("Imputed dataset saved as 'combined_labor_market_analysis_data_imputed.csv'\n")
cat("Number of observations:", nrow(final_dataset_complete), "\n")
cat("Number of variables:", ncol(final_dataset_complete), "\n\n")
```

## 9. Test Robustness of Your DiD Model

```{r did-robustness}
# # Run different specifications of your DiD model
# 
# # Base model
# model1 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median + did_top10 + did_top25,
#             data = final_dataset_complete)
# 
# # With controls
# model2 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median +
#                unemployment_rate_winsorized + offshoring_per_1000_employees_combined + did_top10 + did_top25 ,
#             data = final_dataset_complete)
# 
# # With imputed union data
# model3 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median + 
#                unemployment_rate_winsorized + offshoring_per_1000_employees_combined + did_top10 + did_top25,
#             data = final_dataset_complete)
# 
# # # With fixed effects using factors
# # model4 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median +
# #                unemployment_rate_winsorized + offshoring_per_1000_employees_combined + 
# #                factor(naics_2digit) + factor(year),
# #             data = final_dataset_complete)
# 
# # With fixed effects using factors
# model4 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + h1b_dependency_preperiod + avg_preperiod_dependency + did_median + factor(naics_2digit) + inflation_rate + did_top10 + did_top25,
#             data = final_dataset_complete)
# 
# # Compare models
# model_comparison <- list(
#   Original = model1,
#   With_Controls = model2,
#   With_Union = model3,
#   With_FE = model4
# ) %>%
#   lapply(tidy) %>%
#   bind_rows(.id = "model") %>%
#   # filter(term %in% c("denial_rate", "high_dependency_median", "did_median")) %>%
#   select(model, term, estimate, std.error, p.value)
# 
# print(model_comparison)
```
## 9*. Model using Stargazing

```{r}
library(stargazer)
library(broom)
library(dplyr)

# # Run different specifications of your DiD model
# # Base model
# # model1 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
# #              h1b_dependency_preperiod +  
# #              did_median + did_top10 + did_top25, 
# #              data = final_dataset_complete)
# 
# # # With controls
# # model2 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
# #              h1b_dependency_preperiod + 
# #              did_median + unemployment_rate_winsorized + 
# #              offshoring_per_1000_employees_combined + inflation_rate +
# #              did_top10 + did_top25, 
# #              data = final_dataset_complete)
# # 
# # # With imputed union data
# # model3 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
# #              h1b_dependency_preperiod +  
# #              did_median + unemployment_rate_winsorized + 
# #              offshoring_per_1000_employees_combined + inflation_rate +
# #              union_pct_combined +
# #              did_top10 + did_top25, 
# #              data = final_dataset_complete)
# # 
# # # With fixed effects using factors
# # model4 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
# #              h1b_dependency_preperiod +  
# #              did_median + inflation_rate + 
# #              factor(naics_2digit), 
# #              data = final_dataset_complete)
# 
# # # With fixed effects (industry and time) using factors and controls
# # model6 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
# #              h1b_dependency_preperiod + 
# #              did_median + inflation_rate + 
# #               offshoring_per_1000_employees_combined + 
# #               unemployment_rate_winsorized +
# #              factor(naics_2digit) + factor(year), 
# #              data = final_dataset_complete)
# 
# # With fixed effects using factors and controls
# model1 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
#              h1b_dependency_preperiod + 
#              did_median + inflation_rate + 
#                offshoring_per_1000_employees_combined + 
#               unemployment_rate_winsorized +
#              factor(naics_2digit), 
#              data = final_dataset_complete)
# 
# # With fixed effects using factors and controls
# model2 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
#              h1b_dependency_preperiod + 
#              inflation_rate + 
#                offshoring_per_1000_employees_combined + 
#               unemployment_rate_winsorized +
#              factor(naics_2digit) + did_top25, 
#              data = final_dataset_complete)
# 
# # Create a publication-ready table using stargazer
# # Output to HTML for better formatting in reports/documents
# stargazer_output <- stargazer(model1, model2,
#                       title = "Regression Results: Impact of H-1B Visa Restrictions on Wages",
#                       column.labels = c("With FE and Controls", "FE (Time and Industry + Control") ,
#                       dep.var.labels = "Log Real Wage",
#                       # covariate.labels = c("DiD Median", "Denial Rate"
#                       #                     ,"Unemployment Rate", "Offshoring per 1000 Employees"),
#                       omit = c("factor"),
#                       omit.stat = c("f", "ser"),
#                       notes = "Note: Fixed effects for industry (NAICS 2-digit) included in Model 4 but not shown.",
#                       notes.append = FALSE,
#                       model.numbers = TRUE,
#                       digits = 3,
#                       header = FALSE,
#                       type = "text")
# 
# # Write the HTML output to a file
# writeLines(stargazer_output, "regression_results.html")
# 
# # # Save to HTML file
# # cat(key_table_formatted, file = "key_results_table.html")
```
##9** Cleaned Models:
```{r clean model}
library(stargazer)
library(broom)
library(dplyr)

# With fixed effects using factors
model1 <- lm(log_real_wage ~ did_median  + denial_rate + 
             unemployment_rate_winsorized +
             offshoring_per_1000_employees_combined + 
             factor(naics_2digit), 
             data = final_dataset_complete)

# With fixed effects using factors and controls
model2 <- lm(log_real_wage ~ did_median  + denial_rate + 
             unemployment_rate_winsorized +
             offshoring_per_1000_employees_combined + 
             factor(naics_2digit) + factor(year), 
             data = final_dataset_complete)

# Create a dummy variable for NAICS 54 (Professional Services)
final_dataset_complete <- final_dataset_complete %>%
  mutate(naics_54 = ifelse(naics_2digit == "54", 1, 0))

# Also create an interaction term between NAICS 54 and denial rate
final_dataset_complete <- final_dataset_complete %>%
  mutate(naics54_denial_rate = naics_54 * denial_rate)

model3 <- lm(log_real_wage ~ naics_54 + denial_rate + naics54_denial_rate +
             unemployment_rate_winsorized +
             offshoring_per_1000_employees_combined + 
             factor(year), 
             data = final_dataset_complete)

# Create a publication-ready table using stargazer
stargazer_output <- stargazer(model1, model2, model3,
                      title = "Regression Results: Impact of H-1B Visa Restrictions on Wages",
                      column.labels = c("Median Dependency With Industry FE", "Median Dependency With Industry and Year FEs", "NAICS 54 vs Others"),
                      dep.var.labels = "Log Real Wage",
                      covariate.labels = c("DiD Median", "NAICS 54 (Professional Services)","Denial Rate", 
                                           "NAICS 54 × Denial Rate", 
                                           "Unemployment Rate", 
                                           "Offshoring per 1000 Employees"),
                                        
                      omit = c("factor","Constant"),
                      omit.stat = c("f", "ser"),
                      notes = "Note: Fixed effects for industry (NAICS 2-digit) included but not shown. Significance levels: * p<0.1, ** p<0.05, *** p<0.01.",
                      notes.append = FALSE,
                      model.numbers = TRUE,
                      digits = 3,
                      header = FALSE,
                      type = "text")

# Write the output to a file
writeLines(stargazer_output, "regression_results.html")
```
## 9**** Model Industry 54:
```{r}
library(dplyr)
library(stargazer)

# Subset the data to only include NAICS code 54
industry54_data <- final_dataset_complete %>%
  filter(naics_2digit == "54")

# Create a post-treatment indicator for after the 2017 policy
industry54_data <- industry54_data %>%
  mutate(post_policy = ifelse(year > 2017, 1, 0))

# Run time series models for industry 54
model_ind54_time <- lm(log_real_wage ~ post_policy + denial_rate, 
                       data = industry54_data)

model_ind54_controls <- lm(log_real_wage ~ post_policy + denial_rate + unemployment_rate_winsorized +
                          offshoring_per_1000_employees_combined, 
                          data = industry54_data)

# Generate table for industry 54 specific models
ind54_table <- stargazer(model_ind54_time, model_ind54_controls, 
                         # model_ind54_trend,
                     title = "Effects of H-1B Visa Restrictions on Industry 54",
                     column.labels = c("Basic", "With Controls", "With Trends"),
                     dep.var.labels = "Log Real Wage",
                     # covariate.labels = c("Post-Policy (2017+)", "Denial Rate", 
                     #                     "Inflation Rate", "Unemployment Rate", 
                     #                     "Offshoring per 1000 Employees",
                     #                     "Time Trend",
                     #                     "Post-Policy Trend"),
                     omit.stat = c("f", "ser"),
                     notes = "Analysis restricted to Industry 54 (Professional, Scientific, and Technical Services). Significance levels: * p<0.1, ** p<0.05, *** p<0.01.",
                     notes.append = FALSE,
                     model.numbers = TRUE,
                     digits = 3,
                     header = FALSE,
                     type = "text")

writeLines(ind54_table, "industry54_analysis.html")
```

```{r results='asis'}
# # Load required libraries
# library(ggplot2)
# library(dplyr)
# library(scales)
# library(gridExtra)
# library(tidyr)
# 
# # ----- PART 1: Create Conceptual DiD Diagram -----
# # Create sample data for DiD visualization
# treatment_data <- data.frame(
#   time = rep(c("Pre-treatment", "Post-treatment"), 2),
#   group = rep(c("High H-1B Dependency", "Low H-1B Dependency"), each = 2),
#   value = c(4.8, 6.8, 3.0, 4.2),  # Pre/Post values for Treatment, then Pre/Post for Control
#   counterfactual = c(NA, 6.0, NA, NA)  # Counterfactual for treatment group
# )
# 
# # Convert variables to factors with specific ordering
# treatment_data$time <- factor(treatment_data$time, levels = c("Pre-treatment", "Post-treatment"))
# treatment_data$group <- factor(treatment_data$group, levels = c("High H-1B Dependency", "Low H-1B Dependency"))
# 
# # Create the conceptual DiD plot
# did_concept <- ggplot(treatment_data, aes(x = time, y = value, group = group, color = group)) +
#   geom_line(size = 1.2) +
#   geom_point(size = 3) +
#   geom_line(data = treatment_data %>% filter(!is.na(counterfactual)), 
#             aes(y = counterfactual), linetype = "dashed", size = 1.2) +
#   annotate("segment", x = 2, xend = 2, y = 6.0, yend = 6.8, 
#            arrow = arrow(length = unit(0.3, "cm")), color = "black") +
#   annotate("text", x = 2.03, y = 6.4, label = "Treatment\nEffect", hjust = 0) +
#   geom_text(data = treatment_data %>% filter(time == "Post-treatment" & group == "High H-1B Dependency"),
#             aes(label = "Actual", y = value + 0.4), color = "black", vjust = 0) +
#   geom_text(data = treatment_data %>% filter(time == "Post-treatment" & group == "High H-1B Dependency"),
#             aes(label = "Counterfactual", y = counterfactual - 0.4), color = "black", vjust = 1) +
#   scale_y_continuous(
#     name = "Real Wage",
#     limits = c(0, 10),
#     breaks = seq(0, 10, by = 2),
#     labels = function(x) paste0("$", x, "k")
#   ) +
#   scale_color_manual(values = c("High H-1B Dependency" = "#2C3E92", "Low H-1B Dependency" = "#E07932")) +
#   labs(
#     title = "Difference-in-Differences Estimation",
#     subtitle = "Impact of H-1B Visa Restrictions on Wages",
#     x = "",
#     color = "Industry Group"
#   ) +
#   theme_minimal() +
#   theme(
#     legend.position = "bottom",
#     panel.grid.minor = element_blank(),
#     plot.title = element_text(face = "bold", size = 14),
#     plot.subtitle = element_text(size = 12),
#     axis.title.y = element_text(face = "bold"),
#     legend.title = element_text(face = "bold")
#   ) +
#   geom_vline(xintercept = 1.5, linetype = "dotted", color = "gray50")
# 
# # Print the conceptual diagram
# print(did_concept)
# ggsave("did_concept_diagram.png", did_concept, width = 8, height = 6, dpi = 300)
# 
# # ----- PART 2: Create Data-Driven DiD Visualization -----
# # Load your data 
# # Note: Replace this with your actual data loading code
# data <- read.csv("combined_labor_market_analysis_data_imputed.csv", stringsAsFactors = FALSE)
# 
# # Ensure correct data types
# data$year <- as.numeric(data$year)
# data$real_wage <- as.numeric(data$real_wage)
# data$log_real_wage <- as.numeric(data$log_real_wage)
# data$high_dependency_median <- as.logical(data$high_dependency_median)
# data$high_dependency_top25 <- as.logical(data$high_dependency_top25)
# data$high_dependency_top10 <- as.logical(data$high_dependency_top10)
# data$post_treatment <- as.logical(data$post_treatment)
# 
# # 1. Calculate average wages by year and dependency group
# wage_trends <- data %>%
#   group_by(year, post_treatment) %>%
#   summarize(
#     # Median split
#     high_dep_real_wage = mean(real_wage[high_dependency_median], na.rm = TRUE),
#     low_dep_real_wage = mean(real_wage[!high_dependency_median], na.rm = TRUE),
#     high_dep_log_wage = mean(log_real_wage[high_dependency_median], na.rm = TRUE),
#     low_dep_log_wage = mean(log_real_wage[!high_dependency_median], na.rm = TRUE),
#     
#     # Top 25% split
#     high_dep25_real_wage = mean(real_wage[high_dependency_top25], na.rm = TRUE),
#     low_dep25_real_wage = mean(real_wage[!high_dependency_top25], na.rm = TRUE),
#     high_dep25_log_wage = mean(log_real_wage[high_dependency_top25], na.rm = TRUE),
#     low_dep25_log_wage = mean(log_real_wage[!high_dependency_top25], na.rm = TRUE),
#     
#     # Top 10% split
#     high_dep10_real_wage = mean(real_wage[high_dependency_top10], na.rm = TRUE),
#     low_dep10_real_wage = mean(real_wage[!high_dependency_top10], na.rm = TRUE),
#     high_dep10_log_wage = mean(log_real_wage[high_dependency_top10], na.rm = TRUE),
#     low_dep10_log_wage = mean(log_real_wage[!high_dependency_top10], na.rm = TRUE)
#   )
# 
# # 2. Calculate counterfactual trends
# # Function to predict linear trend
# predict_trend <- function(pre_data, years) {
#   model <- lm(value ~ year, data = pre_data)
#   return(predict(model, newdata = data.frame(year = years)))
# }
# 
# # Prepare pre-treatment data for trend estimation
# pre_data_median <- wage_trends %>%
#   filter(!post_treatment) %>%
#   select(year, high_dep_real_wage, low_dep_real_wage, high_dep_log_wage, low_dep_log_wage)
# 
# # Create long format for easier modeling
# pre_data_high <- pre_data_median %>%
#   select(year, high_dep_real_wage) %>%
#   rename(value = high_dep_real_wage) %>%
#   mutate(group = "High Dependency")
# 
# pre_data_low <- pre_data_median %>%
#   select(year, low_dep_real_wage) %>%
#   rename(value = low_dep_real_wage) %>%
#   mutate(group = "Low Dependency")
# 
# pre_data_combined <- bind_rows(pre_data_high, pre_data_low)
# 
# # Get post-treatment years
# post_years <- wage_trends$year[wage_trends$post_treatment]
# 
# # Predict counterfactual for high dependency group
# high_dep_model <- lm(high_dep_real_wage ~ year, data = pre_data_median)
# high_counterfactual <- predict(high_dep_model, newdata = data.frame(year = post_years))
# 
# # Predict counterfactual for low dependency group
# low_dep_model <- lm(low_dep_real_wage ~ year, data = pre_data_median)
# low_counterfactual <- predict(low_dep_model, newdata = data.frame(year = post_years))
# 
# # Create complete dataset with counterfactuals
# did_visual_data <- wage_trends %>%
#   select(year, post_treatment, high_dep_real_wage, low_dep_real_wage) %>%
#   rename(
#     "High H-1B Dependency" = high_dep_real_wage,
#     "Low H-1B Dependency" = low_dep_real_wage
#   )
# 
# # Add counterfactual values
# counterfactual_data <- data.frame(
#   year = post_years,
#   post_treatment = TRUE,
#   high_counterfactual = high_counterfactual,
#   low_counterfactual = low_counterfactual
# )
# 
# # Join counterfactual data
# did_visual_data <- did_visual_data %>%
#   left_join(counterfactual_data, by = c("year", "post_treatment"))
# 
# # Convert to long format for plotting
# did_long <- did_visual_data %>%
#   pivot_longer(
#     cols = c("High H-1B Dependency", "Low H-1B Dependency"),
#     names_to = "group",
#     values_to = "actual_value"
#   )
# 
# # Add indicator for whether to display counterfactual
# did_long <- did_long %>%
#   mutate(
#     counterfactual_value = case_when(
#       group == "High H-1B Dependency" & post_treatment ~ high_counterfactual,
#       group == "Low H-1B Dependency" & post_treatment ~ low_counterfactual,
#       TRUE ~ NA_real_
#     )
#   )
# 
# # 3. Create the DiD visualization with actual data
# did_plot <- ggplot(did_long, aes(x = year, color = group)) +
#   # Actual lines
#   geom_line(aes(y = actual_value, group = group), size = 1.2) +
#   geom_point(aes(y = actual_value), size = 3) +
#   
#   # Counterfactual lines
#   geom_line(aes(y = counterfactual_value, group = paste0(group, "_cf")), 
#             linetype = "dashed", size = 1.2) +
#   
#   # Add vertical line for policy implementation
#   geom_vline(xintercept = 2017, linetype = "dashed", color = "gray50") +
#   annotate("text", x = 2017, y = max(did_long$actual_value, na.rm = TRUE) * 1.05, 
#            label = "Buy American,\nHire American", hjust = 0) +
#   
#   # Label for treatment effect
#   annotate("segment", 
#            x = 2020, xend = 2020, 
#            y = did_long$counterfactual_value[did_long$year == 2020 & did_long$group == "High H-1B Dependency"],
#            yend = did_long$actual_value[did_long$year == 2020 & did_long$group == "High H-1B Dependency"],
#            arrow = arrow(length = unit(0.3, "cm")), color = "black") +
#   
#   # Customize scales and labels
#   scale_y_continuous(
#     name = "Average Real Wage ($)",
#     labels = dollar_format(prefix = "$")
#   ) +
#   scale_color_manual(values = c("High H-1B Dependency" = "#2C3E92", "Low H-1B Dependency" = "#E07932")) +
#   scale_x_continuous(breaks = 2012:2020) +
#   
#   labs(
#     title = "Impact of \"Buy American, Hire American\" on Industry Wages",
#     subtitle = "Difference-in-Differences Analysis (2012-2020)",
#     x = "Year",
#     color = "Industry Group"
#   ) +
#   theme_minimal() +
#   theme(
#     legend.position = "bottom",
#     panel.grid.minor = element_blank(),
#     plot.title = element_text(face = "bold", size = 14),
#     plot.subtitle = element_text(size = 12),
#     axis.title = element_text(face = "bold"),
#     legend.title = element_text(face = "bold")
#   )
# 
# # Print the DiD plot
# print(did_plot)
# ggsave("h1b_did_analysis.png", did_plot, width = 10, height = 7, dpi = 300)
# 
# # ----- PART 3: Create a version with log wages -----
# # Create similar plot for log wages
# # Similar steps but using log wage variables
# 
# # ----- PART 4: Create DiD Regression Table -----
# # Run different specifications of your DiD model
# # Base model
# model1 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
#              h1b_dependency_preperiod + avg_preperiod_dependency + 
#              did_median + did_top10 + did_top25, 
#              data = data)
# 
# # With controls
# model2 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
#              h1b_dependency_preperiod + avg_preperiod_dependency + 
#              did_median + unemployment_rate_winsorized + 
#              offshoring_per_1000_employees_combined + inflation_rate +
#              did_top10 + did_top25, 
#              data = data)
# 
# # With fixed effects for industry
# model3 <- lm(log_real_wage ~ denial_rate + h1b_dependency_current + 
#              h1b_dependency_preperiod + avg_preperiod_dependency + 
#              did_median + unemployment_rate_winsorized + 
#              offshoring_per_1000_employees_combined + inflation_rate +
#              did_top10 + did_top25 + 
#              factor(naics_2digit), 
#              data = data)
# 
# # Create regression table
# # Note: You'll need to install stargazer if not already installed
# # install.packages("stargazer")
# library(stargazer)
# 
# # Output to text format
# stargazer(model1, model2, model3,
#           title = "Regression Results: Impact of H-1B Visa Restrictions on Wages",
#           column.labels = c("Base Model", "With Controls", "With Fixed Effects"),
#           dep.var.labels = "Log Real Wage",
#           covariate.labels = c("Denial Rate", "H-1B Dependency (Current)", 
#                               "H-1B Dependency (Pre-Period)", "Avg Pre-Period Dependency",
#                               "DiD Median", "Unemployment Rate", 
#                               "Offshoring per 1000 Employees",
#                               "Inflation Rate", "DiD Top 10%", "DiD Top 25%"),
#           omit = c("factor"),
#           omit.stat = c("f", "ser"),
#           notes = "Note: Fixed effects for industry (NAICS 2-digit) included in Model 3 but not shown.",
#           notes.append = FALSE,
#           model.numbers = TRUE,
#           digits = 3,
#           type = "text",
#           out = "h1b_regression_results.txt")
```
## 10. Visualize Key Findings

```{r visualize-findings}
# # Create a visualization of the DiD effect
# 
# # Prepare data for visualization
# plot_data <- final_dataset_complete %>%
#   group_by(year, high_dependency_median) %>%
#   summarize(avg_log_wage = mean(log_real_wage, na.rm = TRUE),
#             avg_denial_rate = mean(denial_rate, na.rm = TRUE),
#             .groups = "drop") %>%
#   mutate(treatment_group = ifelse(high_dependency_median, "High H-1B Dependency", "Low H-1B Dependency"))
# 
# # Plot the DiD
# ggplot(plot_data, aes(x = year, y = avg_log_wage, color = treatment_group, group = treatment_group)) +
#   geom_line(size = 1) +
#   geom_vline(xintercept = 2017, linetype = "dashed", color = "red") +
#   annotate("text", x = 2017, y = min(plot_data$avg_log_wage), label = "Buy American, Hire American", 
#            angle = 90, vjust = -0.5, hjust = -0.2) +
#   theme_minimal() +
#   labs(
#     title = "Difference-in-Differences: Log Real Wage by H-1B Dependency",
#     subtitle = "Before and After the 'Buy American, Hire American' Executive Order",
#     x = "Year",
#     y = "Average Log Real Wage",
#     color = "Industry Group"
#   )
# ggsave("did_event_study.png", width = 10, height = 7, dpi = 300)
```
## 11. Prediction graphs for 54:
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)

target_naics <- "51"  # Change this to your industry of interest (Professional Services)

# Filter dataset to only include the selected industry
industry_data <- final_dataset_complete %>%
  filter(naics_2digit == target_naics)

# Create a prediction dataset spanning your time range
years <- unique(final_dataset_complete$year)
pred_data <- expand.grid(
  year = years,
  naics_2digit = "51"  # Just use one industry for predictions
)

#print(unique(final_dataset_complete$naics_2digit)[1])

# Get average values for control variables to use in predictions
avg_controls <- industry_data %>%
  group_by(year) %>%
  summarize(
    unemployment_rate_winsorized = mean(unemployment_rate_winsorized, na.rm = TRUE),
    inflation_rate = mean(inflation_rate, na.rm = TRUE),
    offshoring_per_1000_employees_combined = mean(offshoring_per_1000_employees_combined, na.rm = TRUE),
    denial_rate = mean(denial_rate, na.rm = TRUE)
  )

# Merge averages into prediction data
pred_data <- merge(pred_data, avg_controls, by = "year")

# Create specialized datasets for individual effect components
# 1. Denial Rate effect
denial_effect <- pred_data %>%
  mutate(
    effect_value = denial_rate * coef(model2)["denial_rate"],
    effect_type = "Denial Rate Effect"
  )

# 2. Offshoring effect
offshoring_effect <- pred_data %>%
  mutate(
    effect_value = offshoring_per_1000_employees_combined * coef(model2)["offshoring_per_1000_employees_combined"],
    effect_type = "Offshoring Effect"
  )

# 3. Did_median effect (ONLY after 2017) - Create two separate datasets
# First dataset: Pre-2017 (will be NA)
did_effect_pre <- pred_data %>%
  filter(year < 2017) %>%
  mutate(
    effect_value = NA,  # Set to NA so no line will be drawn
    effect_type = "H-1B Dependency Effect (Post-2017)"
  )

# Second dataset: 2017 and after (with actual values)
did_effect_post <- pred_data %>%
  filter(year >= 2017) %>%
  mutate(
    effect_value = coef(model2)["did_median"],  # Apply the coefficient
    effect_type = "H-1B Dependency Effect (Post-2017)"
  )

# Combine all effect datasets
effects_data <- bind_rows(
  denial_effect %>% select(year, effect_value, effect_type),
  offshoring_effect %>% select(year, effect_value, effect_type),
  did_effect_pre %>% select(year, effect_value, effect_type),
  did_effect_post %>% select(year, effect_value, effect_type)
)

custom_colors <- c(
  "Denial Rate Effect" = "#1f77b4",           # Blue
  "Offshoring Effect" = "#2ca02c",            # Green
  "H-1B Dependency Effect (Post-2017)" = "#d62728"  # Red
)

# Create the visualization
ggplot() +
  # Add effect lines
  geom_line(data = effects_data, 
            aes(x = year, y = effect_value, color = effect_type, linetype = "solid"),
            size = 1, na.rm = TRUE) +  # na.rm=TRUE ensures NA values don't connect
  
  # Add a point at the start of the H-1B dependency effect (2017)
  geom_point(data = did_effect_post %>% filter(year == 2017),
             aes(x = year, y = effect_value, color = effect_type),
             size = 4) +
  
  # Add vertical line for 2017 policy
  geom_vline(xintercept = 2017, color = "red", linetype = "dashed", size = 1) +
  
  # Add policy label
  annotate("text", x = 2013.8, y = max(effects_data$effect_value, na.rm = TRUE),
           label = "'Buy American, Hire American'",
           hjust = 0, vjust = 1, color = "red", fontface = "bold") +
  
  # Format the plot
  scale_color_manual(values = custom_colors) +
  scale_y_continuous(limits = c(0, 0.15), breaks = seq(0, 0.1, by = 0.025)) +
  scale_x_continuous(breaks = years) +
  labs(
    title = "Predicted Wage Effects from H-1B Visa Restrictions",
    subtitle = "Component Effects Based on Regression Model",
    x = "Year",
    y = "Effect on Log Real Wage",
    color = "Effect Component",
    linetype = "Effect Component"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    axis.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(fill = NA, color = "gray80")
  )

# # Save the plot
ggsave("h1b_wage_effects_51.png", width = 10, height = 7, dpi = 300)
```

## 11. Prediction graphs for 72:
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)

# Create a prediction dataset spanning your time range
years <- unique(final_dataset_complete$year)
pred_data <- expand.grid(
  year = years,
  naics_2digit = "72"  # Just use one industry for predictions
)
print(unique(final_dataset_complete$naics_2digit)[1])

# Get average values for control variables to use in predictions
avg_controls <- final_dataset_complete %>%
  group_by(year) %>%
  summarize(
    unemployment_rate_winsorized = mean(unemployment_rate_winsorized, na.rm = TRUE),
    inflation_rate = mean(inflation_rate, na.rm = TRUE),
    offshoring_per_1000_employees_combined = mean(offshoring_per_1000_employees_combined, na.rm = TRUE),
    denial_rate = mean(denial_rate, na.rm = TRUE)
  )

# Merge averages into prediction data
pred_data <- merge(pred_data, avg_controls, by = "year")

# Create specialized datasets for individual effect components
# 1. Denial Rate effect
denial_effect <- pred_data %>%
  mutate(
    effect_value = denial_rate * coef(model2)["denial_rate"],
    effect_type = "Denial Rate Effect"
  )

# 2. Offshoring effect
offshoring_effect <- pred_data %>%
  mutate(
    effect_value = offshoring_per_1000_employees_combined * coef(model2)["offshoring_per_1000_employees_combined"],
    effect_type = "Offshoring Effect"
  )

# 3. Did_median effect (ONLY after 2017) - Create two separate datasets
# First dataset: Pre-2017 (will be NA)
did_effect_pre <- pred_data %>%
  filter(year < 2017) %>%
  mutate(
    effect_value = NA,  # Set to NA so no line will be drawn
    effect_type = "H-1B Dependency Effect (Post-2017)"
  )

# Second dataset: 2017 and after (with actual values)
did_effect_post <- pred_data %>%
  filter(year >= 2017) %>%
  mutate(
    effect_value = coef(model2)["did_median"],  # Apply the coefficient
    effect_type = "H-1B Dependency Effect (Post-2017)"
  )

# Combine all effect datasets
effects_data <- bind_rows(
  denial_effect %>% select(year, effect_value, effect_type),
  offshoring_effect %>% select(year, effect_value, effect_type),
  did_effect_pre %>% select(year, effect_value, effect_type),
  did_effect_post %>% select(year, effect_value, effect_type)
)

custom_colors <- c(
  "Denial Rate Effect" = "#1f77b4",           # Blue
  "Offshoring Effect" = "#2ca02c",            # Green
  "H-1B Dependency Effect (Post-2017)" = "#d62728"  # Red
)

# Create the visualization
ggplot() +
  # Add effect lines
  geom_line(data = effects_data,
            aes(x = year, y = effect_value, color = effect_type, linetype = "solid"),
            size = 1, na.rm = TRUE) +  # na.rm=TRUE ensures NA values don't connect

  # Add a point at the start of the H-1B dependency effect (2017)
  geom_point(data = did_effect_post %>% filter(year == 2017),
             aes(x = year, y = effect_value, color = effect_type),
             size = 4) +

  # Add vertical line for 2017 policy
  geom_vline(xintercept = 2017, color = "red", linetype = "dashed", size = 1) +

  # Add policy label
  annotate("text", x = 2013.8, y = max(effects_data$effect_value, na.rm = TRUE),
           label = "'Buy American, Hire American'",
           hjust = 0, vjust = 1, color = "red", fontface = "bold") +

  # Format the plot
  scale_color_manual(values = custom_colors) +
  scale_y_continuous(limits = c(0, 0.1), breaks = seq(0, 0.1, by = 0.025)) +
  scale_x_continuous(breaks = years) +
  labs(
    title = "Predicted Wage Effects from H-1B Visa Restrictions",
    subtitle = "Component Effects Based on Regression Model",
    x = "Year",
    y = "Effect on Log Real Wage",
    color = "Effect Component",
    linetype = "Effect Component"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    axis.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(fill = NA, color = "gray80")
  )

# # Save the plot
ggsave("h1b_wage_effects_72.png", width = 10, height = 7, dpi = 300)
```

```{r}
# Create subset for NAICS 54 only
naics54_data <- final_dataset_complete %>% 
  filter(naics_2digit == "54")

# Create subset for all other industries
other_industries_data <- final_dataset_complete %>% 
  filter(naics_2digit != "54")

# Run the same model on both subsets
model_naics54 <- lm(log_real_wage ~ denial_rate + inflation_rate + 
                    unemployment_rate_winsorized + 
                    offshoring_per_1000_employees_combined + 
                    factor(year), 
                    data = naics54_data)

model_others <- lm(log_real_wage ~ denial_rate + inflation_rate + 
                   unemployment_rate_winsorized + 
                   offshoring_per_1000_employees_combined + 
                   factor(year), 
                   data = other_industries_data)

# Create a publication-ready table using stargazer
stargazer_output <- stargazer(model_naics54, model_others,
                      title = "Regression Results: Impact of H-1B Visa Restrictions on Wages",
                      column.labels = c("Median Dependency With Industry FE", "Median Dependency With Industry and Year FEs", "NAICS 54 vs Others"),
                      dep.var.labels = "Log Real Wage",
                      # covariate.labels = c("DiD Median", "NAICS 54 (Professional Services)","Denial Rate", 
                      #                      "NAICS 54 × Denial Rate", 
                      #                      "Unemployment Rate", 
                      #                      "Offshoring per 1000 Employees"),
                                        
                      omit = c("factor","Constant"),
                      omit.stat = c("f", "ser"),
                      notes = "Note: Fixed effects for industry (NAICS 2-digit) included but not shown. Significance levels: * p<0.1, ** p<0.05, *** p<0.01.",
                      notes.append = FALSE,
                      model.numbers = TRUE,
                      digits = 3,
                      header = FALSE,
                      type = "text")

# Write the output to a file
writeLines(stargazer_output, "regression_results.html")
```

